\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}  
\addtolength{\evensidemargin}{-0.5in} 
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in} %.5
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\Huge Grant Gurvis} & \large{Email: \href{mailto:ggurvis@usf.edu}{ggurvis@usf.edu}}\\
        \Large{\href{https://ggurvis.com}{ggurvis.com}} & \large{Phone: (904)~536--5040}\\
             & \large{Tampa, FL}
     \end{tabular*}

     \vspace{1em}

%--P

%\section{Professional Summary}
%I am a Junior Computer Science student graduating in Fall 2021 seeking an internship or research opportunity for the upcoming summer or fall.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of South Florida}{Tampa, Florida}
      {Computer Science, Minor in Mathematics, GPA: 3.35 Comp Sci GPA: 3.58
      }{August 2018 -- December 2021}
      \resumeItemListStart
        \resumeItem{Select Coursework}
        {Computer Architecture, Object Orientated Design, Data Structures,
          Analysis of Algorithms, Operating Systems, Automata Theory,
          AI (Spring `21), and Compilers (Spring `21) }
      \resumeItemListEnd
  %\resumeSubheading
  %    {Paxon School for Advanced Studies}{Jacksonville, Florida}
  %    {International Baccalaureate Diploma; Cum Laude}{Aug. 2014 -- May. 2018}
  %    \resumeItemListStart
  %    \resumeItem{Involvement}
  %    {President of Philosophy Club, Brain Brawl Competitor, and T.V. Production Director}
  %    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {USF Society of Aeronautics and Rocketry}{Tampa, Florida}
      {IREC Payload Lead and Chief Technical Officer}{November 2018 -- present}
      \resumeItemListStart
        \resumeItem{\href{https://github.com/usfsoar/irec-avionics-payload-pcb}{IREC Payload Lead}}
          {Created a payload for a sounding rocket that is planned to go 30,000' which has a custom altimeter with a microwave radio to send telemetry to ground during flight.} 
          \resumeItem{Chief Technical Officer}
          {Created a \href{https://soarsite.netlify.app/}{new
          website} for the organization as well as designed promotion material.}
        \resumeItem{Outreach}
          {Volunteered at multiple events to help under privileged students and Girl Scouts to earn a mechanical engineering badge through learning about rockets and engineering.}
          %\resumeItem{TRA Level 1 Certification} 
          %{Certified with TRA to launch rockets with up to 640 newton-seconds of impulse}
       \resumeItemListEnd

    %\resumeSubheading
    %  {Five Alive Films}{Jacksonville, Florida}
    %  {Editor and Photographer}{Oct. 2016 -- July. 2018}
    %  \resumeItemListStart
    %    \resumeItem{Editing}
    %    {Created the closing animated credits, reedited and colorized \textit{Missy’s Musical Misadventure}.}
    %    \resumeItem{Photography}
    %      {Photographer for a documentary film shoot on the Jacksonville Axemen Rugby Team.}
    %  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS---------------
\section{Projects}

  \resumeSubHeadingListStart
      \resumeSubItem{\href{https://github.com/grant0417/ray_tracer}{Ray Tracer}} 
      {A path tracer that supports parallel execution, .obj loading, BVH
        acceleration with a command line interface that will support most file
      types for output as well as a WASM based site.}
    \resumeSubItem{\href{https://github.com/grant0417/emu6502}{6502 Emulator}}
      {Implemented full 6502 instruction set emulated in Rust that supports all indexing modes and is accurate to the cycle. Supports extendability via easily implementable memory maps. }
    \resumeSubItem{\href{https://github.com/grant0417/assembler6502}{6502 Assembler}}
      {Implemented 6502 assembler in Rust that allows for flexibility in the assembly while still being able to assemble into a binary for the emulator or hex codes plus a debug mode.}
      \resumeItem{\href{}{Vote Chair}}
      {A voting website designed for the UCF Knight Hacks 2020 Hackaton.
    Designed the front end using React and back end using Express.}
    \resumeSubItem{\href{https://github.com/grant0417/meme-bot}{Machine Learning Meme Generator}}
      {Used Keras and Tensorflow with Python to predict what would follow based on training on the book Moby Dick, then formated that prediction in a standard meme format. Won second place in the USF HackJam hackathon in November 2019.}
  \resumeSubHeadingListEnd


%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {C, C++, Rust, Python, Java, C\#, Haskell}
      \resumeSubItem{Web}
      {HTML5, CSS, Javascript, TypeScript, React, Express, WebAssembly} 
    \resumeSubItem{Creative Software}
      {Premiere Pro, After Effects, Photoshop, Illustrator, GIMP,
      Inkscape}
    \resumeSubItem{Git}
      {Git with GitHub/GitLab}
    \resumeSubItem{Operating Systems}
    {GNU/Linux(Arch, Ubuntu), Windows, macOS}
    \resumeSubItem{\LaTeX}
      {This resume was written in \LaTeX}
    \resumeSubItem{3D Graphics Software}
      {Fusion 360, Blender, Unity, Unreal Engine}
  \resumeSubHeadingListEnd

\end{document}
